Pre- and Post-Debate Democratic Primary Data: Twitter, Google Trends, and Polls

### 2019-12-08 Presentation/SURV727_FinalPresentation_Padgett_Thiam.Rmd
update intro

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

>>>>

- Can Twitter data and Google trends data be used to supplement polling results, by providing real-time information to candidates while they wait for polling data to come in?
- Exploratory analysis to see if pre- and post-debate polling data during the 2020 U.S. Democratic primary election aligns with these real-time sources
